---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo=FALSE
)
```

Install the __outlierfix__ package for setting up
```{r setup}
library(devtools)
install_github("sssEos/outlierfix")
library(outlierfix)
```

Let us create some sample data for fixing outliers later.
```{r}
library(data.table)
dt <- data.table(age= c(89,23, 26, 21, 31, 38, 34, 25, 65,32, 36 ,38, 35 ,30 ,35, 20,11),income=c(1200,1400,1350,1600,7580,3620,2500,4230,4830,3820,5230,3360,2860,3120,2970,3000,4500))
dt
```
### 1. Detecting and fixing outliers in an interactive way
Firstly, we focus on the __age__, set the age limit within 20-60, which make more sense for working age. Enter the number of chosen method for identifying outliers, we try 1 and according to the histogram and boxplot of data to choose the subsequent fix method (enter number)
```{r}
fixout_conti(dt, col_name="age",rangeLU=c(20,60))
```
### 2. Detecting and fixing outliers in an automatic way
choose column __income__ to fix the outliers automatically. In this case, we want to have all figures in range but exclude the income equals to 1200. Missing values are excluded in default.
```{r}
fixout_conti(dt, col_name="income",interactive = FALSE,exclude=1200)
```
Save the output as new data table.
```{r}
dt1=fixout_conti(dt, col_name="income",interactive = FALSE,exclude=1200)
dt1
```
This function can be used to process multiple columns in a data table when leveraging loop. It is worth noting this approach is not suitable when the fixed method related to "drop" because some rows of data has been dropped while processing sequentially.
```{r}
col_names <- c("age", "income" )
fix.m <-c("asNARight", "asNALeft" )
dt1 <- dt
#remove outliers 
for( i in 1: length(col_names)){
  dt1=fixout_conti(dt1,col_name=col_names[i], fix.m = fix.m[i])
}
```



