---
title: "R Notebook"
output: html_notebook
---
Install the __outlierfix__ package for setting up
```{r setup}
library(devtools)
install_github("sssEos/outlierfix")
library(outlierfix)
```

Let us create some sample data for fixing outliers later.
```{r}
library(data.table)
dt <- data.table(age= c(89,23, 26, 21, 31, 38, 34, 25, 65,32, 36 ,38, 35 ,30 ,35, 20,11),income=c(1200,1400,1350,1600,7580,3620,2500,4230,4830,3820,5230,3360,2860,3120,2970,3000,4500))
dt
```
### 1. Detecting and fixing outliers in an interactive way
Firstly, we focus on the __age__, set the age limit within 20-60, which make more sense for working age. Enter the number of chosen method for identifying outliers, we try 1 and according to the histogram and boxplot of data to choose the subsequent fix method (enter number)
```{r}
fixout_conti(dt, col_name=col_name,rangeLU=c(20,60),interactive = TRUE)
```
### 2. Detecting and fixing outliers in an automatic way
choose column __income__ to fix the outliers automatically. In this case, we want to have all figures in range but exclude the income equals to 1200. Missing values are excluded in default.
```{r}
fixout_conti(dt, col_name="income",interactive = FALSE,exclude=1200)
```
Save the output as new data table.
```{r}
dt1=fixout_conti(dt, col_name="income",interactive = FALSE,exclude=1200)
dt1
```




